Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2018-11-16 man/tables/t_dendro_summary.Rmd
update tables

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
```

@@

```{r, echo=FALSE}
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)

@@

t2 <- t1raw %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(8:13), round, 3) %>% 
  unite(length_year, c(length_year,length_year5), sep=" (") %>%
  unite(RW, c(rw_mean,rw_std), sep=" (") %>%
  mutate(
    length_year = paste0(length_year, pare),
    RW = paste0(RW, pare)) %>% 
  dplyr::select(name, first_year, last_year, 
  length_year, n_trees, n_radii,
  RW, ms2, ar1, rbar.wt, eps, -pare, -site)

colnames(t2) <- c("Site", "First year", "Last year", "Length (years)",  
                   "# trees", '# cores', "RW (mm)", "MS", "AR(1)", "Rbt", "EPS")

pander(t2,
       split.table = Inf)

>>>>

---
output:
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
```

@@

```{r}
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)

@@

t2 <- t1raw %>% 
  mutate(pare = ")") %>% 
  mutate_at(c(8:13), round, 3) %>% 
  unite(length_year, c(length_year,length_year5), sep=" (") %>%
  mutate_at(.vars = c("rw_mean","rw_std"), funs(formatC(., digits = 3, format = 'f'))) %>% 
  unite(RW, c(rw_mean,rw_std), sep=" (") %>%
  mutate(
    length_year = paste0(length_year, pare),
    RW = paste0(RW, pare)) %>% 
  dplyr::select(name, first_year, last_year, 
  length_year, n_trees, n_radii,
  RW, ms2, ar1, rbar.wt, eps, -pare, -site)

ta2 <- regulartable(t2, col_keys =c("name", "first_year", "last_year", "n_trees", "n_radii", "RW", "ms2",
                                   "ar1","rbar.wt","eps"))
ta2 <- ta2 %>% set_header_labels(name = "Site", first_year = "First year", last_year = "Last year",
                                 length_year = "Length (years)", n_trees ="# trees", n_radii = '# cores',
                                 RW ="RW (mm)", ms2="MS", ar1="AR(1)", rbar.wt = "Rbt", eps = "EPS") %>%
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 10) %>% 
  fontsize(part = "body", size = 9) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  align(align = "center")

ta2

### 2018-11-16 man/tables/t_droughts.Rmd
update tables

---
output: 
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE, dpi = 200)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")

library("grid")
library("gridExtra")
library("patchwork")
library("ggcorrplot")
library("stringr")
library("pander")
library("lemon")
library("viridis")
library("ggthemes")
```

```{r, echo=FALSE}
show_text <- FALSE
```

>>>>

---
output: 
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_pagebreak.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library("tidyverse")
library("here")
library("dplyr")
library("flextable")

```

### 2018-11-16 man/tables/t_huber_res_bai.Rmd
update tables

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, echo = FALSE, warning = FALSE}

# Number of digits 
d <- 3

@@

mt <- regulartable(mi, col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))
mt <- mt %>% 
  # Header 
  set_header_labels(site = "Sites", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience") %>% 
  add_header(site="", '2005rt' = "2005", '2005rc' = "2005", '2005rs' = "2005",'2012rt' = "2012", '2012rc' = "2012", '2012rs' = "2012",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "", top = TRUE) %>% 
  merge_at(i = 1, j =c(3:5) , part = "header") %>% 
  merge_at(i = 1, j =c(7:9) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 12) %>%

  # General format 
  fontsize(part = "body", size = 11) %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(align = "center") %>%

>>>>

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

@@

```{r}
# Number of digits 
d <- 3

@@

mt <- regulartable(mi, col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))
mt <- mt %>% 
  # Header 
  set_header_labels(site = "Sites", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience") %>% 
  add_header(site="", '2005rt' = "2005", '2005rc' = "2005", '2005rs' = "2005",'2012rt' = "2012", '2012rc' = "2012", '2012rs' = "2012",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "", top = TRUE) %>% 
  merge_at(i = 1, j =c(3:5) , part = "header") %>% 
  merge_at(i = 1, j =c(7:9) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 9) %>%

  # General format 
  fontsize(part = "body", size = 8) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  empty_blanks() %>% 
  align(align = "center") %>%

### 2018-11-16 man/tables/t_huber_res_evi.Rmd
update tables

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library('officer')
```

@@

```{r, echo = FALSE, warning = FALSE}

@@

mt <- regulartable(mi, col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))
mt <- mt %>% 
  # Header 
  set_header_labels(site = "Oak populations", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience") %>% 
  add_header(site="", '2005rt' = "2005", '2005rc' = "2005", '2005rs' = "2005",'2012rt' = "2012", '2012rc' = "2012", '2012rs' = "2012",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "", top = TRUE) %>% 
  merge_at(i = 1, j =c(3:5) , part = "header") %>% 
  merge_at(i = 1, j =c(7:9) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 12) %>%

  # General format 
  fontsize(part = "body", size = 11) %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(align = "center") %>%

>>>>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library('officer')
```

@@

```{r}

@@

mt <- regulartable(mi, col_keys = c("site","c1", "2005rt","2005rc","2005rs", "c2",
                                "2012rt","2012rc","2012rs","c3","2099rt","2099rc", "2099rs"))
mt <- mt %>% 
  # Header 
  set_header_labels(site = "Oak populations", 
                        '2005rt' = "Resistance", '2005rc' = "Recovery", '2005rs' = "Resilience",
                        '2012rt' = "Resistance", '2012rc' = "Recovery", '2012rs' = "Resilience",
                        '2099rt' = "Resistance", '2099rc' = "Recovery", '2099rs' = "Resilience") %>% 
  add_header(site="", '2005rt' = "2005", '2005rc' = "2005", '2005rs' = "2005",'2012rt' = "2012", '2012rc' = "2012", '2012rs' = "2012",
                        '2099rt' = "", '2099rc' = "", '2099rs' = "", top = TRUE) %>% 
  merge_at(i = 1, j =c(3:5) , part = "header") %>% 
  merge_at(i = 1, j =c(7:9) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 9) %>%

  # General format 
  fontsize(part = "body", size = 8) %>% 
  autofit(add_w = 0, add_h = 0) %>% 
  empty_blanks() %>% 
  align(align = "center") %>%

### 2018-11-16 man/tables/t_robust_anovas.Rmd
update tables

---
output:  
  pdf_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
```

@@

```{r, echo=FALSE, include = FALSE}
### Table R1_evi
evi <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(evi) <- c('factores', 'F', 'p', 'variables')

@@

```{r, echo=FALSE}
# # https://haozhu233.github.io/kableExtra/use_kableExtra_with_formattable.html
# colnames(dff) <- c("variable", "factors", "F", "p", "F", "p", "F", "p")
# colnames(dff) <- c("variable", "factors", "rt\nF", "rt\np","rc\nF", "rc\np", "rs\nF", "rs\np")
# kable(dff, format = "latex") %>% add_header_above(c("", "", "Resistance" = 2, "Recovery" = 2, "Resilience" = 2))
#

# https://davidgohel.github.io/flextable/articles/examples.html

mt <- regulartable(
  data = dff, 
  col_keys = c("variable", "factores", "c3","rt_F", "rt_p", "c1", "rc_F", "rc_p","c2", "rs_F", "rs_p"),
)

mt <- theme_vanilla(mt)
mt <- autofit(mt)
mt <- empty_blanks(mt)
mt <- align(mt, j = 1,  align = "center")

mt <- merge_v(mt, ~variable)

mt <- set_header_labels(mt, variable = "", factores = "", rt_F = "Resistance", rt_p = "Resistance", rc_F = "Recovery", rc_p = "Recovery", rs_F = "Resilience", rs_p = "Resilience")

# # Add row of labels 
mt <- add_header(mt, variable = "Variable", factores = "Factor", rt_F = "F", rt_p = "p", rc_F = "F", rc_p = "p", rs_F = "F", rs_p = "p", top = FALSE)

# Format 
mt <- bold(mt, part = 'header') 
mt <- fontsize(mt, part = "header", size = 12)
mt <- fontsize(mt, part = "body", size = 11)
mt <- width(mt, j = 2, width = 2)

# mt <- align(mt, i = 1, j=2:3, align = "left")

mt <- italic(mt, i = ~ rt_p < 0.01, j = ~ rt_p)
mt <- italic(mt, i = ~ rc_p < 0.01, j = ~ rc_p)
mt <- italic(mt, i = ~ rs_p < 0.01, j = ~ rs_p)
mt

mt <- set_formatter(mt, 
                    rt_F = function(x) format(round(x, 1)),
                    rc_F = function(x) format(round(x, 1)),
                    rs_F = function(x) format(round(x, 1))
                    )

mt

>>>>

---
output:
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
library(officer)
```

@@

```{r}
### Table R1_evi
evi <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)
names(evi) <- c('factores', 'F', 'p', 'variables')

@@

```{r}
mt <- regulartable(
  data = dff, 
  col_keys = c("variable", "factores", "c3","rt_F", "rt_p", "c1", "rc_F", "rc_p","c2", "rs_F", "rs_p"),
)

mti <- mt %>% 
  autofit() %>% 
  empty_blanks() %>% 
  align(j = 1,  align = "center") %>% 
  merge_v(~variable) %>% 
  set_header_labels(variable = "", factores = "", rt_F = "Resistance", rt_p = "Resistance", rc_F = "Recovery", rc_p = "Recovery", rs_F = "Resilience", rs_p = "Resilience") %>% 
  add_header(variable = "Variable", factores = "Factor", rt_F = "F", rt_p = "p", rc_F = "F", rc_p = "p", rs_F = "F", rs_p = "p", top = FALSE) %>% 
  bold(part = 'header') %>% 
  fontsize(part = "header", size = 12) %>%
  fontsize(part = "body", size = 11) %>% 
  width(j = 2, width = 2) %>% 
  italic(i = ~ rt_p < 0.01, j = ~ rt_p) %>% 
  italic(i = ~ rc_p < 0.01, j = ~ rc_p) %>% 
  italic(i = ~ rs_p < 0.01, j = ~ rs_p)
mti

# mt <- set_formatter(mt, 
#                     rt_F = function(x) format(round(x, 1)),
#                     rc_F = function(x) format(round(x, 1)),
#                     rs_F = function(x) format(round(x, 1))
#                     ) 
# 
# mt

### 2018-11-16 man/tables/t_sampled_plots.Rmd
update tables

---
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: ../template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
```

@@

```{r, echo=FALSE}
topo <- read.csv(here::here("/data/sites_summary", "site_general.csv"), header = TRUE)
ages <- read.csv(here::here("/data/dendro_summary", "site3_avg_ages.csv"), header = TRUE)
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)
biotic <- read.csv(here::here("/data/competence", "biotic_stand_features.csv"), header = TRUE)
letritas <- read.csv(here::here("/out/kw_stand_features", "kw_letras.csv"), header = TRUE)

@@

t1 <- t1raw %>% dplyr::select(
  name, lat_m, long_m, elev_min, elev_max, slope_mean, slope_sd, prec, temp, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, srd_mean, srd_sd,
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l, srd_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c("lat_m","long_m","slope_mean","slope_sd","ba_mean","ba_sd","srd_mean","srd_sd"), 
            funs(formatC(., digits = 2,format='f'))) %>%  
  # mutate_at(c(10:19, 22:23), round, 1) %>% 
  mutate_at(c("dn_mean","dn_sd","h_mean","h_sd","age_mean","age_std","dn_mean_all","dn_sd_all","h_mean_all","h_sd_all","stand_density_mean","stand_density_sd"),
            funs(formatC(., digits = 1,format='f'))) %>%
  mutate_at(c("elev_min", "elev_max"), funs(round(., 0))) %>% 
  unite(elev, c(elev_min, elev_max), sep= " - ") %>% 
  unite(slope, c(slope_mean, slope_sd), sep=" (") %>% 
  unite(n_trees, c(n_trees, n_radii), sep=" (") %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  unite(srd, c(srd_mean, srd_sd), sep=" (") %>% 
  mutate(
    slope = paste0(slope, pare),
    n_trees = paste0(n_trees, pare),
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste0(age, pare),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' '),
    srd = paste(paste0(srd, pare), srd_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l, -srd_l)

colnames (t1) <- c("Site", "Lat (&deg;)", "Long (&deg;)", "Elevation (m)", "Slope (&deg;)", 
                   "Prec. (mm)", "Temp (&deg; C)",
                   "# trees (# cores)", "Dbh (cm)", "Height (m)", "Age (years)", 
                   "Dbh all (cm)", "Height all (m)", "BA (m2/ha)", "Density (trees/ha)", "SRD")

pander(t1, split.table = Inf)

>>>>

---
output:
  word_document:
    fig_caption: yes
    highlight: null
    reference_docx: ../../templates/template_tables_portrait.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecology.csl
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(pander)
library(kableExtra)
library(knitr)
library(dplyr)
library(flextable)
```

@@

```{r}
topo <- read.csv(here::here("/data/sites_summary", "site_general.csv"), header = TRUE)
ages <- read.csv(here::here("/data/dendro_summary", "site3_avg_ages.csv"), header = TRUE)
dendro_summ <- read.csv(here::here("/data/dendro_summary", "site3_dendro_summary.csv"), header = TRUE)
biotic <- read.csv(here::here("/data/competence", "biotic_stand_features.csv"), header = TRUE)
letritas <- read.csv(here::here("/out/kw_stand_features", "kw_letras.csv"), header = TRUE)

@@

t1 <- t1raw %>% dplyr::select(
  name, lat_m, long_m, elev_min, elev_max, slope_mean, slope_sd, prec, temp, 
  n_trees, n_radii, dn_mean, dn_sd, h_mean, h_sd, age_mean, age_std, 
  dn_mean_all, dn_sd_all, h_mean_all, h_sd_all,
  ba_mean, ba_sd, stand_density_mean, stand_density_sd, srd_mean, srd_sd,
  all_dn_l, all_h_l, ba_l, ft_dn_l, ft_h_l, std_l, srd_l
  ) %>% 
  mutate(pare = ")") %>% 
  mutate_at(c("lat_m","long_m","slope_mean","slope_sd","ba_mean","ba_sd","srd_mean","srd_sd"), 
            funs(formatC(., digits = 2,format='f'))) %>%  
  mutate_at(.vars = c("prec"), funs(format(., digits = 0))) %>% 
  # mutate_at(c(10:19, 22:23), round, 1) %>% 
  mutate_at(c("dn_mean","dn_sd","h_mean","h_sd","age_mean","age_std","dn_mean_all","dn_sd_all","h_mean_all","h_sd_all","stand_density_mean","stand_density_sd"),
            funs(formatC(., digits = 1,format='f'))) %>%
  mutate_at(c("elev_min", "elev_max"), funs(round(., 0))) %>% 
  unite(elev, c(elev_min, elev_max), sep= " - ") %>% 
  unite(slope, c(slope_mean, slope_sd), sep=" (") %>% 
  unite(n_trees, c(n_trees, n_radii), sep=" (") %>% 
  unite(dn, c(dn_mean, dn_sd), sep=" (") %>% 
  unite(h, c(h_mean, h_sd), sep=" (") %>% 
  unite(age, c(age_mean, age_std), sep=" (") %>% 
  unite(dn_all, c(dn_mean_all, dn_sd_all), sep=" (") %>% 
  unite(h_all, c(h_mean_all, h_sd_all), sep=" (") %>% 
  unite(ba, c(ba_mean, ba_sd), sep=" (") %>% 
  unite(stand_density, c(stand_density_mean, stand_density_sd), sep=" (") %>% 
  unite(srd, c(srd_mean, srd_sd), sep=" (") %>% 
  mutate(
    slope = paste0(slope, pare),
    n_trees = paste0(n_trees, pare),
    dn = paste(paste0(dn, pare), ft_dn_l, sep=" "),
    h = paste(paste0(h, pare), ft_h_l, sep = ' '),
    age = paste0(age, pare),
    dn_all = paste(paste0(dn_all, pare), all_dn_l, sep = ' '),
    h_all = paste(paste0(h_all, pare), all_h_l, sep = ' '),
    ba = paste(paste0(ba, pare), ba_l, sep = ' '),
    stand_density = paste(paste0(stand_density, pare), std_l, sep = ' '),
    srd = paste(paste0(srd, pare), srd_l, sep = ' ')) %>%
  dplyr::select(-pare, -all_dn_l, -all_h_l, -ba_l, -ft_dn_l, -ft_h_l, -std_l, -srd_l)

ta <- regulartable(t1, col_keys =c("name", "lat_m", "long_m", "elev", "slope", "prec", "temp",
                                   "n_trees","dn","h","age","dn_all","h_all","ba","stand_density","srd"))

ta <- ta %>% set_header_labels(name = "Site", lat_m = "Lat (\u00B0)", long_m = "Long (\u00B0)", 
                               elev = "Elevation\n(m)", slope = "Slope (\u00B0)",  prec = "Prec.\n(mm)",
                               temp = "Temp.\n(\u00B0 C)", n_trees = "# trees\n(# cores)", dn = "Dbh (cm)",
                               h = "Height\n(m)", age = "Age\n(years)", dn_all = "Dbh all\n(cm)", 
                               h_all = "Height all\n(m)", ba = "BA\n(m2/ha)", 
                               stand_density = "Density\n(trees/ha)", srd = "SRD") %>% 
  add_header(name="", lat_m ="", long_m="", elev="", slope ="", prec = "", temp = "",
             n_trees = "Cored trees", dn = "Cored trees", h = "Cored trees", age = "Cored trees", 
             dn_all = "Competence", h_all = "Competence", ba = "Competence", 
             stand_density = "Competence", srd = "Competence", top = TRUE) %>% 
  merge_at(i = 1, j =c(8:11) , part = "header") %>% 
  merge_at(i = 1, j =c(12:16) , part = "header") %>% 
  align(align = "center", part = "header") %>% 
  bold(part = 'header') %>% 
  fontsize(i= 1, part = "header", size = 8) %>% 
  fontsize(i= 2, part = "header", size = 8) %>% 
  italic(i=1, part = "header") %>% 
    # General format 
  fontsize(part = "body", size = 7) %>% 
  autofit(add_w = 0) %>% 
  align(align = "center") %>% 
  width(j = c(2,3), width = 0.35) %>% 
  width(j = c(6,7,8), width = 0.6)

ta
